\vspace{-.5cm} Lights: a generalized joint model for high-dimensional multivariate longitudinal data and censored durations \vspace{.5cm}

### 2022-01-31 manuscript/paper.tex
Update the assumption about dependency of latent variables

We suppose a group-specific marker trajectory and a generalized linear mixed model for each longitudinal marker given subgroup $G$, so that for the $l$-th outcome at time $t \geq 0$ one has
\begin{equation}
	\label{eq:link-function}
 	h_l\big(\E[Y^l(t)|b^l, G=k]\big) = m_k^l(t)
 \end{equation}
where $h_l$ denotes a known one-to-one link function, and $m_k^l$ the linear predictor such that
\[ m_k^l(t) = u^l(t)^\top\beta_k^l + v^l(t)^\top b^l \]
where $u^l(t) \in \R^{q_l}$ is a row vector of (possibly) time-varying features with corresponding unknown fixed effect parameters $\beta_k^l$, and $v^l(t) \in \R^{r_l}$ is a row vector of (possibly) time-varying features with $r_l \leq q_l$ and where the corresponding subject-and-longitudinal outcome specific random effects $b^l$ that does not depend on the group membership, which is not a strong modeling assumption.
\begin{assumption}
\label{assumption1}
We suppose that the random effects are independent of the group membership, and that the latter remain independent conditional on the observed data (namely $T$, $\Delta$ and $Y$).
\end{assumption}
A suitable distributional assumption for the random effects component is a zero-mean multivariate normal distribution~\citep{hickey2016joint}, that is
\begin{equation}
   \label{eq:random-effect-law}
   b^l \sim \cN(0, D_{ll})
 \end{equation} 
with $D_{ll} \in \R^{r_l \times r_l}$ the unstructured variance-covariance matrix. 
To account for dependence between the different longitudinal outcome types, we let $\text{Cov}[b^l,b^{l'}] = D_{ll'}$ for $l \ne l'$ and we denote
\[ D = 
\begin{bmatrix}
  D_{11} & \cdots & D_{1L}\\
  \vdots &  \ddots & \vdots \\
  D_{1L}^\top & \cdots & D_{LL}
\end{bmatrix}
\]
the global variance-covariance matrix.
In the sequel of the paper, our aim is to associate the true and unobserved value $m_k^l(t)$ of the $l$-th longitudinal outcome at time $t$ with the event outcome $T^\star$.

>>>>

We suppose a group-specific marker trajectory and a generalized linear mixed model for each longitudinal marker given subgroup $G$, so that for the $l$-th outcome at time $t \geq 0$ one has
\begin{equation}
	\label{eq:link-function}
 	h_l\big(\E[Y^l(t)|b^l, G=k]\big) = m_k^l(t)
 \end{equation}
where $h_l$ denotes a known one-to-one link function, and $m_k^l$ the linear predictor such that
\[ m_k^l(t) = u^l(t)^\top\beta_k^l + v^l(t)^\top b^l \]
where $u^l(t) \in \R^{q_l}$ is a row vector of (possibly) time-varying features with corresponding unknown fixed effect parameters $\beta_k^l$, and $v^l(t) \in \R^{r_l}$ is a row vector of (possibly) time-varying features with $r_l \leq q_l$ and where the corresponding subject-and-longitudinal outcome specific random effects $b^l$ that does not depend on the group membership, which is not a strong modeling assumption.
\begin{assumption}
\label{assumption1}
We suppose that the random effects are conditional independent of the group membership on the association features, and that the latter remain independent conditional on the observed data (namely $T$, $\Delta$ and $Y$).
\end{assumption}
A suitable distributional assumption for the random effects component is a zero-mean multivariate normal distribution~\citep{hickey2016joint}, that is
\begin{equation}
   \label{eq:random-effect-law}
   b^l \sim \cN(0, D_{ll})
 \end{equation} 
with $D_{ll} \in \R^{r_l \times r_l}$ the unstructured variance-covariance matrix. 
To account for dependence between the different longitudinal outcome types, we let $\text{Cov}[b^l,b^{l'}] = D_{ll'}$ for $l \ne l'$ and we denote
\[ D = 
\begin{bmatrix}
  D_{11} & \cdots & D_{1L}\\
  \vdots &  \ddots & \vdots \\
  D_{1L}^\top & \cdots & D_{LL}
\end{bmatrix}
\]
the global variance-covariance matrix.
In the sequel of the paper, our aim is to associate the true and unobserved value $m_k^l(t)$ of the $l$-th longitudinal outcome at time $t$ with the event outcome $T^\star$.
